---
title: 'Results brms text for ldeli growth'
author: Fonti Kar
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: "Style_guide.docx"
---

```{r setup, include=FALSE, eval = T, echo = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
sessionInfo()

# R version 3.6.1 (2019-07-05)
# Platform: x86_64-apple-darwin15.6.0 (64-bit)
# Running under: macOS High Sierra 10.13.6

pacman::p_load(dplyr, magrittr, ggplot2, patchwork, lubridate, stringr, tidyr, MCMCglmm, bookdown, pander, brms, janitor, purrr, tidybayes, stringr, latex2exp, tidybayes, bayestestR, kinship2)

#Read in dataset
#Complete
data <- read.csv("./data/growth/processed/analysis/Ldeli_quangen_growth_for_analysis.csv", stringsAsFactors = F)
str(data)
dim(data)

#Augmented
data_DA <- read.csv("./data/growth/processed/analysis/Ldeli_quangen_growth_DA.csv", stringsAsFactors = F)
str(data_DA)
dim(data_DA)

#ggplot theme
my_theme <- theme(#legend.position = "none",
  legend.position = "bottom",
  legend.text =element_text(size = 14),
  legend.title =element_text(size = 14, face = "bold"),
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(),
  axis.text=element_text(size=16),
  axis.title=element_text(size=16,face="bold"),
  plot.title = element_text(size = 20, face = "bold", hjust = 0.5))

source("./R/Analysis/brms functions.R")
```

```{r}
#| echo: false
#| warning: false
#| message: false

# Explore pedigree a bit
  data_ped <- data %>% group_by(dam_id)  %>% summarise(n_babes = length(unique(liz_id)), n_sires = length(unique(sire_id))) %>% as.data.frame()

  pedigree_stats <- data %>% group_by(treatment, dam_id, sire_id)  %>% summarise(n_offspring = length(unique(liz_id))) %>% as.data.frame()
```

# Results

```{r, echo = FALSE, include = FALSE}
data %>% nrow()
data %>% select()

#Total number of lizards
data$liz_id %>% unique() %>% length()

#How many lizards per treatment
treat_lizards <- data %>% group_by(treatment) %>%
  summarise(Num_individuals = length(unique(liz_id)))

#How old were lizards
age_dat <-data %>% group_by(liz_id, treatment) %>%
  summarise(max_age = max(days_since_hatch))
age_dat %>% filter(treatment == 29) %>% pull(max_age) %>% mean() %>% round(2)
age_dat %>% filter(treatment == 29) %>% pull(max_age) %>% min() %>% round(2)
age_dat %>% filter(treatment == 29) %>% pull(max_age) %>% max() %>% round(2)

age_dat %>% filter(treatment == 23) %>% pull(max_age) %>% mean() %>% round(2)
age_dat %>% filter(treatment == 23) %>% pull(max_age) %>% min() %>% round(2)
age_dat %>% filter(treatment == 23) %>% pull(max_age) %>% max() %>% round(2)

age_dat %>% pull(max_age) %>% mean() %>% round(2)
age_dat %>% pull(max_age) %>% sd() %>% round(2)

#How many measurements per lizard
num_meas_dat <- data %>% group_by(liz_id, treatment) %>%
  summarise(Num_measures = length(liz_id)) %>% as.data.frame()
mean(num_meas_dat$Num_measures) %>% round(2)
sd(num_meas_dat$Num_measures) %>% round(2)

#Merge 
measures_age <- left_join(num_meas_dat, age_dat) 
measures_age %>% filter(Num_measures >= 11.5) %>% pull(max_age) %>% mean()
measures_age %>% filter(Num_measures >= 11.5) %>% pull(max_age) %>% sd()
```

## Description of dataset
Over two years,  we collected `r data %>% nrow()` observations of mass data for a total of `r data$liz_id %>% unique() %>% length()` individuals ($n_{hot}$ = `r treat_lizards[2,2]`, $n_{cold}$ = `r treat_lizards[1,2]`). The average age for hot incubated lizards was `r age_dat %>% filter(treatment == 29) %>% pull(max_age) %>% mean() %>% round(2)` (range: `r age_dat %>% filter(treatment == 29) %>% pull(max_age) %>% min() %>% round(2)` -- `r age_dat %>% filter(treatment == 29) %>% pull(max_age) %>% max() %>% round(2)`) and for cold incubated lizards it was `r age_dat %>% filter(treatment == 23) %>% pull(max_age) %>% mean() %>% round(2)` (range: `r age_dat %>% filter(treatment == 23) %>% pull(max_age) %>% min() %>% round(2)` -- `r age_dat %>% filter(treatment == 23) %>% pull(max_age) %>% max() %>% round(2)`). On average, a lizard had `r mean(num_meas_dat$Num_measures) %>% round(2)` measurements (SD = `r sd(num_meas_dat$Num_measures) %>% round(2)`).

## The influence of developmental temperature on additive genetic variance and maternal effects across age 

Overall, additive genetic variance, permanent environmental variance and heritability of growth appears to be higher in the hot developmental temperature treatment (Fig. 1). However, there were no significant differences among treatment groups (Table S3). Treatment groups did not differ in how the relative contributions of $G$ and $M$ changed with age as their 95% credible intervals overlapped (Fig. S1). Additive genetic variance remained relatively low and constant upon emergence until approximately nine months of age, after which it increased rapidly (Fig. S1). Maternal effects decreasing sharply upon hatching and dropped to the minimum at approximately six months before it increased (Fig. S1). There were some differences among developmental treatments in how residual variance changed with age (Fig. S1). We investigated whether increases in mass mean over time would result in scale effects that can bias variance estimates. We found that CV of G and M followed the same pattern was the raw variance estimates and conclude that scale effects did not influence our results (Fig. S2).After accounting for heterogenous residual variance, we found no differences in $h^2$ or the proportion of variance explained by maternal effects ($M^2$) (Fig.2). Heritability was very low for the first year of growth in L.deliata and only began increasing at one year of age (Fig. 2). As predicted $M^2$ decreased since hatching, however it increased slightly from six months of age (Fig. 2). The $G$ and $M$ matrices for each treatment group are presented in Table S6-S7.

```{r, echo = FALSE, warning = FALSE, include = FALSE, message = FALSE}
#Marginalised over age - PIE CHART
#Read in intercept models
cold_brm_4.5 <- readRDS("./output/rds/brm_10_cold") #cold_brm_4.5
hot_brm_4.5 <- readRDS("./output/rds/brm_10_hot") #hot_brm_4.5

#Extract VCV
cold_brm_4.5_post <- posterior_samples(cold_brm_4.5) 
hot_brm_4.5_post <- posterior_samples(hot_brm_4.5) 

#Calculate total phenotypic variance for each treatment
Hot_Pheno_intercept <- hot_brm_4.5_post[,"sd_F1_Genotype__Intercept"]^2 +
  hot_brm_4.5_post[,"sd_dam_id__Intercept"]^2 + 
  hot_brm_4.5_post[,"sigma"]^2

cold_Pheno_intercept <- cold_brm_4.5_post[,"sd_F1_Genotype__Intercept"]^2 +
  cold_brm_4.5_post[,"sd_dam_id__Intercept"]^2 + 
  cold_brm_4.5_post[,"sigma"]^2

#Create a table
hot_cold_Vcomps <- as.data.frame(matrix(ncol = 5, nrow = 8))
colnames(hot_cold_Vcomps) <- c("Treatment", "Variable", "Estimate", "Lower", "Upper")

hot_cold_Vcomps$Treatment <- rep(c("Hot", "Cold"), each =5)
hot_cold_Vcomps$Variable <-rep(c("V_additive_g", "V_maternal",  "Vresidual", "h2"), 2)

#Fill in table
hot_cold_Vcomps[1,3:5] <- ((hot_brm_4.5_post[,"sd_F1_Genotype__Intercept"])^2 %>% posterior_summary())[-2] %>% round(3)
hot_cold_Vcomps[2,3:5] <- ((hot_brm_4.5_post[,"sd_dam_id__Intercept"])^2 %>% posterior_summary())[-2]%>% round(3)
hot_cold_Vcomps[3,3:5] <- ((hot_brm_4.5_post[,"sigma"])^2 %>% posterior_summary())[-2]%>% round(3)
hot_cold_Vcomps[4,3:5] <- ((hot_brm_4.5_post[,"sd_F1_Genotype__Intercept"]^2 / Hot_Pheno_intercept) %>% posterior_summary())[-2] %>% round(3)

hot_cold_Vcomps[5,3:5] <- ((cold_brm_4.5_post[,"sd_F1_Genotype__Intercept"])^2 %>% posterior_summary())[-2]%>% round(3)
hot_cold_Vcomps[6,3:5] <- ((cold_brm_4.5_post[,"sd_dam_id__Intercept"])^2 %>% posterior_summary())[-2]%>% round(3)
hot_cold_Vcomps[7,3:5] <- ((cold_brm_4.5_post[,"sigma"])^2 %>% posterior_summary())[-2]%>% round(3)
hot_cold_Vcomps[8,3:5] <- ((cold_brm_4.5_post[,"sd_F1_Genotype__Intercept"]^2 / cold_Pheno_intercept) %>% posterior_summary())[-2]%>% round(3)

#Plot this
wesanderson::wes_palette("Darjeeling2") %>% str()

cold_pieplot <- hot_cold_Vcomps %>% filter(Treatment == "Cold"  & ! Variable == "h2")

ggplot(cold_pieplot, aes(y = Estimate, x = "", fill = Variable)) + 
  geom_bar(stat="identity", width=1)  + 
  coord_polar("y", start=0) + 
  scale_fill_manual(values = c("#046C9A", "#D69C4E" ,"#ABDDDE", "#000000")) + 
  theme_void() 

hot_pieplot <- hot_cold_Vcomps %>% filter(Treatment == "Hot" & ! Variable == "h2")

ggplot(hot_pieplot, aes(y = Estimate, x = "", fill = Variable)) + 
  geom_bar(stat="identity", width=1)  + 
  coord_polar("y", start=0) + 
  scale_fill_manual(values = c("#046C9A", "#D69C4E" ,"#ABDDDE", "#000000")) + 
  theme_void() 

#These were saved as pdf and labels were added via PowerPoint

#Test for differences use p_direction HOT  - COLD
#Overall variance
diff_Pheno_intercept <- Hot_Pheno_intercept - cold_Pheno_intercept
posterior_summary(diff_Pheno_intercept)

#Additive genetic variance
diff_Vg <- (hot_brm_4.5_post[,"sd_F1_Genotype__Intercept"]^2) - (cold_brm_4.5_post[,"sd_F1_Genotype__Intercept"])^2
posterior_summary(diff_Vg)

#Maternal variance
diff_Vm <- (hot_brm_4.5_post[,"sd_dam_id__Intercept"]^2) - (cold_brm_4.5_post[,"sd_dam_id__Intercept"])^2
posterior_summary(diff_Vm)

#Residual variance
diff_Ve <- (hot_brm_4.5_post[,"sigma"]^2) - (cold_brm_4.5_post[,"sigma"])^2
posterior_summary(diff_Ve)

#h2
diff_h2 <- (hot_brm_4.5_post[,"sd_F1_Genotype__Intercept"]^2 / Hot_Pheno_intercept) - (cold_brm_4.5_post[,"sd_F1_Genotype__Intercept"]^2 / cold_Pheno_intercept)
posterior_summary(diff_h2)

```

```{r, echo = FALSE, warning = FALSE, message = FALSE, include = FALSE}
#Estimating h2 and m2 over age
cold_brm_5.5 <- readRDS("./output/rds/brm_12_cold_het") #cold_brm_5.5
 hot_brm_5.5 <- readRDS("./output/rds/brm_12_hot_het") #hot_brm_5.5

#Define the days
z_days <- ztran_DsH(seq(0, 500, 30))

#Compiling heritability and maternal effects estimates across days
#Hot developmental temperature model
brms_hot_h2 <- lapply(z_days, function(x) brms_h2(model = hot_brm_5.5, x = x)) %>% bind_rows()
brms_hot_m2 <- lapply(z_days, function(x) brms_m2(model = hot_brm_5.5, x = x)) %>% bind_rows()

#Putting it together in one data frame
brms_hot_h2m2 <- bind_rows(brms_hot_h2, 
                           brms_hot_m2)

#Assigning treatment
brms_hot_h2m2$treatment <- "hot"

#Cold developmental temperature model
brms_cold_h2 <- lapply(z_days, function(x) brms_h2(model = cold_brm_5.5, x = x)) %>% bind_rows()
brms_cold_m2 <- lapply(z_days, function(x) brms_m2(model = cold_brm_5.5, x = x)) %>% bind_rows()

#Putting it together in one data frame
brms_cold_h2m2 <- bind_rows(brms_cold_h2, 
                            brms_cold_m2)

#Assigning treatment
brms_cold_h2m2$treatment <- "cold"

#Putting hot and cold values together into one dataframe for plotting
brms_h2m2 <- bind_rows(brms_hot_h2m2, brms_cold_h2m2)

#Plotting figure
brms_top_2 <- ggplot(data = brms_h2m2 %>% filter(group_id == "h2"), aes(x = day, y = Estimate, colour = factor(treatment))) +
  geom_point(size = 2) + 
  geom_ribbon(aes(ymin = Lower, ymax = Upper), alpha = 0.05) +
  geom_line(size = 1) + 
  scale_x_continuous(breaks = seq(0, 500, 60)) + 
  scale_y_continuous(lim = c(0,0.1)) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) + 
  labs(x = " ",
       y = TeX("h^2"),
       #title = "Relative contribution of variance over age",
       colour =  "Treatment") + 
  theme_bw() + 
  my_theme +
  theme(legend.position = "none",
        strip.text = element_text(size = 18),
        strip.background = element_blank())

brms_bottom_2 <- ggplot(data = brms_h2m2 %>% filter(group_id == "m2"), aes(x = day, y = Estimate, colour = factor(treatment))) +
  geom_point(size = 2) + 
  geom_ribbon(aes(ymin = Lower, ymax = Upper), alpha = 0.05) +
  geom_line(size = 1) + 
  scale_x_continuous(breaks = seq(0, 500, 60)) + 
  scale_y_continuous(lim = c(0,0.25)) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) + 
  labs(y = TeX("M^2"),
       x = "Age",
       colour = "Treatment") + 
  theme_bw() + 
  my_theme +
  theme(legend.position = "none",
        strip.text = element_text(size = 18),
        strip.background = element_blank())

plot_layout(brms_top_2 / brms_bottom_2)
```

## Do growth rate curves differ between incubation treatments? 

```{r, echo = FALSE, include = FALSE}
#Compare WAIC of fixed effect models
#Read in fixed effect models
    brm_5.het <- readRDS("./output/rds/brm_12_het_fixed1") #old_models/brm_5.het
  brm_5.1.het <- readRDS("./output/rds/brm_12_het_fixed2") #old_models/brm_5.1.het
brm_5.1.5.het <- readRDS("./output/rds/brm_12_het_fixed3") #old_models/brm_5.1.5.het
  brm_5.2.het <- readRDS("./output/rds/brm_12_het_fixed4") #old_models/brm_5.2.het

#Add the WAIC
    waic_5.het <- waic(brm_5.het)
  waic_5.1.het <- waic(brm_5.1.het)
waic_5.1.5.het <- waic(brm_5.1.5.het)
  waic_5.2.het <- waic(brm_5.2.het)

# LOO
    loo_5.het <- loo(brm_5.het, "loo", moment_match = TRUE)
  loo_5.1.het <- loo(brm_5.1.het, "loo", moment_match = TRUE)
loo_5.1.5.het <- loo(brm_5.1.5.het,  "loo", moment_match = TRUE)
  loo_5.2.het <- loo(brm_5.2.het, "loo", moment_match = TRUE)

#Compare
tab_fixed <- loo_compare(waic_5.het, waic_5.1.het, waic_5.1.5.het, waic_5.2.het)

#Tabulating
fixed_waic <- data.frame(matrix(nrow = 4, ncol = 4))
colnames(fixed_waic) <- c("Fixed Effects Formula", "wAIC", "elpd_diff", "se_diff")

fixed_waic[1,1] <- c("Treatment + Age + Age^2 + Treatment*Age + Treatment*Age^2") 
fixed_waic[2,1] <- c("Treatment + Age + Age^2 + Treatment*Age")
fixed_waic[3,1] <- c("Treatment + Age + Age^2+ Treatment*Age^2")
fixed_waic[4,1] <- c("Treatment + Age + Age^2") 

#waic estimates
#wAIC values
fixed_waic[1,2] <- waic_5.het$estimates[3,1]
fixed_waic[2,2] <- waic_5.1.het$estimates[3,1]
fixed_waic[3,2] <- waic_5.1.5.het$estimates[3,1]
fixed_waic[4,2] <- waic_5.2.het$estimates[3,1]

#Expected log predictive density diff
fixed_waic[1,3] <- loo_compare(waic_5.het, waic_5.1.het, waic_5.1.5.het, waic_5.2.het)[1,1] %>% round(3)
fixed_waic[2,3] <- loo_compare(waic_5.het, waic_5.1.het, waic_5.1.5.het, waic_5.2.het)[2,1] %>% round(3)
fixed_waic[3,3] <- loo_compare(waic_5.het, waic_5.1.het, waic_5.1.5.het, waic_5.2.het)[3,1] %>% round(3)
fixed_waic[4,3] <- loo_compare(waic_5.het, waic_5.1.het, waic_5.1.5.het, waic_5.2.het)[4,1] %>% round(3)

#SE diff
fixed_waic[1,4] <- loo_compare(waic_5.het, waic_5.1.het, waic_5.1.5.het, waic_5.2.het)[1,2] %>% round(3)
fixed_waic[2,4] <- loo_compare(waic_5.het, waic_5.1.het, waic_5.1.5.het, waic_5.2.het)[2,2] %>% round(3)
fixed_waic[3,4] <- loo_compare(waic_5.het, waic_5.1.het, waic_5.1.5.het, waic_5.2.het)[3,2] %>% round(3)
fixed_waic[4,4] <- loo_compare(waic_5.het, waic_5.1.het, waic_5.1.5.het, waic_5.2.het)[4,2] %>% round(3)
```

```{r, echo = FALSE}
pander(fixed_waic,
       justify = "lccc",
       #split.cell = 80,
       caption = "Table X Comparison of WAIC values of three models with different combinations of interactions with incubation treatment and  growth curve parameters")
```

```{r, echo = FALSE, include = FALSE}

#Calculating inital mass
summary(brm_5.het)
brm_5.het_post <- posterior_samples(brm_5.het)
colnames(brm_5.het_post)[1:21]

#Overall linear growth rate
growth_rate <- brm_5.het_post["b_z_days_since_hatch"] %>% exp() %>% posterior_summary() %>% round(3)


#Cold coefficients
cold_intercept <- brm_5.het_post[,"b_Intercept"] %>% exp()
posterior_summary(cold_intercept)
mean(cold_intercept)

#Hot coefficients
hot_intercept <- (brm_5.het_post[,"b_Intercept"] + brm_5.het_post[,"b_treatment29"]) %>% exp()
posterior_summary(hot_intercept)
mean(hot_intercept)

#Difference
diff <- round(cold_intercept - hot_intercept, 3)
diff_CI_lower <- posterior_summary(diff)[3]
diff_CI_upper <-posterior_summary(diff)[4]
```

```{r, echo = FALSE, include = FALSE}
#Calculating the age when mass is max
colnames(brm_5.het_post)[1:21]

age <- brm_5.het_post[,"b_z_days_since_hatch"] 
age2 <- brm_5.het_post[,"b_z_days_since_hatch_I2"] 
treat_age <- brm_5.het_post[,"b_treatment29:z_days_since_hatch"]
treat_age2 <- brm_5.het_post[,"b_treatment29:z_days_since_hatch_I2"]
  
#Get AgeMax from model # x = -b / 2a, where b is the coefficient of the linear part, and a is the coefficient of the quadratic part. 
# - sign represents a convex curve, ie it has a maxima
# Note that calculation will be in units of your x variable (i.e z scores)
#See: https://sciencing.com/minmax-quadratic-equation-7723159.html for equation breakdown

hot_zAge_max <- -(age + treat_age) / (2*(age2 + treat_age2)) #Adding treatment effect in units of the x variable in model
hot_Age_max <- (hot_zAge_max * sd(data$days_since_hatch)) + mean(data$days_since_hatch) #Back transform
posterior_summary(hot_Age_max)[1] %>% round(2)
posterior_summary(hot_Age_max)[3] %>% round(2)
posterior_summary(hot_Age_max)[4] %>% round(2)

cold_zAge_max <- -(age) / (2*(age2)) 
cold_Age_max <- (cold_zAge_max * sd(data$days_since_hatch)) + mean(data$days_since_hatch) 
posterior_summary(cold_Age_max)[1] %>% round(2)
posterior_summary(cold_Age_max)[3] %>% round(2)
posterior_summary(cold_Age_max)[4] %>% round(2)
```

While the model containing an full interaction between treatment and linear and quadratic age was best supported, the improvement was marginal (Table 1). Moreover, the linear growth rate (Age) and curvature of the growth trajectory ($Age^2$) did not differ significantly between the two developmental temperature treatments (Table S5, Table S7-S9). Irrespective of treatment, a lizard mass increased by `r growth_rate[1]`g for every 1 SD unit increase in age. Developmental temperature did however impact initial mass (Table 1, Fig. 3). Lizards from the ???cold??? treatment were on average `r mean(diff)`g (95% CI: `r diff_CI_lower`g ??? `r diff_CI_upper`g) heavier compared to lizards from the ???hot??? treatment (Table. 2). Larger initial masses meant that lizards from the ???cold??? treatment reached their maximum mass slightly earlier (`r posterior_summary(cold_Age_max)[1] %>% round(2)` days, 95% CI: `r posterior_summary(cold_Age_max)[3] %>% round(2)` ??? `r posterior_summary(cold_Age_max)[4] %>% round(2)`) compared to lizards from ???hot??? treatment  (`r posterior_summary(hot_Age_max)[1] %>% round(2)` days, 95% CI: `r posterior_summary(hot_Age_max)[3] %>% round(2)` ??? `r posterior_summary(hot_Age_max)[4] %>% round(2)`). The population G and M matrices and other variance components are presented in Table S5. 


```{r, echo = FALSE, cache = TRUE, warning = FALSE, include = FALSE, cache = TRUE}
#Figure 3 of model predictions showing intercept differences
predat <- data_DA %>% select(liz_id, dam_id, treatment) %>% distinct()
z_days <- ztran_DsH(seq(0, 500, 30))
days <- backztran_DSH(z_days)

df <- bind_rows(lapply(days, function(x) func_growth_predictions(x, predat = predat, posterior = brm_5.het_post)))
```

```{r, echo = FALSE, warning = FALSE}
#Generationg Figure 3
hot_ids <- df %>% filter(treatment == "29") %>% pull(liz_id) %>% unique()
set.seed(6)
hot_plot_ids <- as.character(sample(hot_ids, 20, replace = T))

cold_ids <- df %>% filter(treatment == "23") %>% pull(liz_id) %>% unique()
set.seed(6)
cold_plot_ids <- as.character(sample(cold_ids, 20, replace = T))

df %>% filter(liz_id %in% c(hot_plot_ids, cold_plot_ids)) %>%
  ggplot(
    aes(x = day, y = mean_mass)) + 
  geom_point(aes(color = factor(treatment)), alpha = 0.3) + 
  stat_smooth(aes(group = factor(liz_id)), 
              method = "lm", formula = y ~ x + I(x^2), size = 0.1, se = F, colour = "black", alpha = 0.01) + 
  stat_smooth(aes(colour = factor(treatment)), 
              method = "lm", formula = y ~ x + I(x^2), size = 2, se = F, alpha = 0.01) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) + 
  labs(x = "Age",
       y = "Log transformed Mass",
       #title = "Model predictions N = 40",
       colour =  "Treatment") +
  theme_bw() + 
  my_theme
```



