---
title: "Calculating additive genetic variance and h2"
author: "Fonti Kar"
date: "5/28/2020"
output: html_document
---

```{r setup, include=FALSE, eval = T, echo = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
sessionInfo()

# R version 3.6.1 (2019-07-05)
# Platform: x86_64-apple-darwin15.6.0 (64-bit)
# Running under: macOS High Sierra 10.13.6

pacman::p_load(dplyr, magrittr, ggplot2, patchwork, lubridate, stringr, tidyr, MCMCglmm, bookdown, pander, brms, janitor)

#Read in dataset
#Complete
data <- read.csv("./data/growth/processed/analysis/Ldeli_quangen_growth_for_analysis.csv", stringsAsFactors = F)
str(data)
dim(data)

#Read in models
mod.3.2.DA <- readRDS("./output/rds/mod.3.2.DA")
Sol.3.2.DA <- mod.3.2.DA$Sol
VCV.3.2.DA <- mod.3.2.DA$VCV

#Functions
ztran_DsH <- function(day) {
  (day - mean(data$days_since_hatch, na.rm = T)) / sd(data$days_since_hatch, na.rm = T)
}

backztran_DSH <- function(z_day_since_hatch){
  (z_day_since_hatch * sd(data$days_since_hatch, na.rm = T)) + mean(data$days_since_hatch, na.rm = T)
}
```

From Shin's paper:
Vp = VFixed + Vi + Vrandomeffects + Vr
Vi refers to the total variance explained by individual identity, including random intercept and random slope variance. NB: Vrandomeffects will include dam and permanent environment effects?

Vs refes to total between individual variance explained by random slopes
Vs = Vv * Vx
Vv = ID deviation from pop slope
Vx = Variance in covariate e.g.age, if scales Vx = 1 


Total phenotypic variation in growth
Vp = Vi + Vr ? Is this correct or do we have to include fixed effects as per paper? 
"Adjusted" Vp = Vi + Vdam + Vresiduals ?
Narrow h2 in intercepts =  Vi/Vp ?

#Total phenotypic variance of growth
Question: Do we need to account for the covariance among growth curve parameters? 
```{r}
Vtotal_p <- VCV.3.2.DA[,"(Intercept):(Intercept).liz_id"]  + #lizard variance in intercept
  VCV.3.2.DA[,"z_days_since_hatch:z_days_since_hatch.liz_id"] + #lizard variance in slope
  VCV.3.2.DA[,"I(z_days_since_hatch^2):I(z_days_since_hatch^2).liz_id"] + #lizard variance in curve
  VCV.3.2.DA[,"(Intercept):(Intercept).dam_id"]  +  #Dam variance in intercept
  VCV.3.2.DA[,"z_days_since_hatch:z_days_since_hatch.dam_id"] + #Dam variance in slope
  VCV.3.2.DA[,"I(z_days_since_hatch^2):I(z_days_since_hatch^2).dam_id"] + #Dam variance in curve
  VCV.3.2.DA[,"units"] #residuals


  # Fonti - I think you need to also add in the covariances, try this simplified version.

  Var_i <- data.frame(VCV.3.2.DA) %>%
              select(c(1,5,9,10,14,18,19))  # Extract variance columns
  Cov_i <- data.frame(VCV.3.2.DA) %>%
              select(-c(1,5,9,10,14,18,19)) # Extract covariance columns

  # Total variance is sum of variances plus the sum of 2 times the covariances. This should give you the TOTAL variance in P (mass), but because this is an estimate of the population parameters it won't match your sample (i.e., lnMass data).
  
  V_total <- rowSums(Var_i) + rowSums(2*Cov_i) 

#############################################################
  ## ATTEMPT 2
#############################################################
  summary(mod.3.2.DA)
  Sol.3.2.DA <- mod.3.2.DA$Sol
  VCV.3.2.DA <- mod.3.2.DA$VCV

  # OK, I actually think that this is actually a little tricker than I originally thought, particularly so because we have quadratics at different grouping terms. Note we have also z transformed age, and this is important. So here we go with each ranom effect seperately

  # Form Shin's paper we know that 
  # Vi,x = V_{u} + 2x*C_{uv} + x^2*V_{v} when we have a SINGLE covariate. So, if we have a quadratic we also need to account for this...I'm not totally sure the right way, but in keeping with logic lets assume it's this:

  #V_{i,x, x2} = V_{a} + 2x*C_{la} + 2x*C_{qa} + 2x*C_{lq} + x^2*V_{l} + x^2*V_{q}?
  # Here is what I don't know, what to do about the quadratic??! Here l = linear slope, q = quadratic slope and a = intercept. So, for each of these random effect groups I belive that we need to actually form this same equation as above. So, lets just assume for G first

  V_liz_g <- data.frame(VCV.3.2.DA) %>%
              select(c(1,5,9))   # Variance in intercept, linear and quadratic slope

  COV_liz_g <- data.frame(VCV.3.2.DA) %>%
              select(c(2,3,6))   # Covariance among intercept, linear and quadratic slope

# Now, we need to build an equation out of it! 
x = 1
V_g <- V_liz_g[1] + (x^2)*V_liz_g[2] + (x^4)*V_liz_g[3] + 
    2*x*COV_liz_g[1]    # Intercept and Linear slope
+ 2*x^2*COV_liz_g[2] # Intercept and Quadratic slope
+ 2*x^3*COV_liz_g[3] # Linear and Quadratic slope

# OK, a little explanation. We were close, but not quite correct in this case. So, fr all the covariances you have to multiple by 2. The reason why is that, for each covariance you have 2 ways to get it. For example, cov(intercept, slope)and cov(slope,intercept). Think about a matrix. The upper and lower triangles. Now, the reason why x^ changes is because for cov(intercept, slope) term you only have 1 x term. For the cov(intercept, quadratic) we have one x term, but that x term is squared. So, hence why we have x^2. Now, for the cov(linear, quadratic), you have two x, one of which is just 1x and the second of which is x^2. So, x * x^2 = x^3. Hence why we have this. The variance term for quadratic is correct because (x^2)^2 = x^4.

## One way to check that the above equation is correct is to simply CHECK THAT DENOMINATOR VARIANCE IN LNMASS for h2 calculations is = or is CLOSE TO lnMASS IN RAW DATA. DENOMINATOR WILL PROBABLY BE BIGGER THAN RESPONSE. Fonti, please check.

head(V_g)

# Now, because x = 0, this is g in the average environment, which is basically just the intercept!
#We can check: V_g ==V_liz_g[1]

# Now, we need to do exactly the same for EACH grouping cluster, lets try damID

  V_dam_g <- data.frame(VCV.3.2.DA) %>%
              select(c(10,14,18))   # Variance in intercept, linear and quadratic slope

  COV_dam_g <- data.frame(VCV.3.2.DA) %>%
              select(c(11, 12, 15))   

V_dam <- V_dam_g[1] + (x^2)*V_dam_g[2] + (x^4)*V_dam_g[3] + 
2*x*COV_dam_g[1]    # Intercept and Linear slope
+ 2*x^2*COV_dam_g[2] # Intercept and Quadratic slope
+ 2*x^3*COV_dam_g[3] # Linear and Quadratic slope

# Residual variance
R <- VCV.3.2.DA[,"units"]

h2 <- V_g / (V_g + V_dam + R)

posterior_summary(h2)
  
#Calculating age-specific heritability (x = 1, which means 1 SD away from mean = 336.841 days ~ a year old) #NB: Use backztran_DSH function


posterior_summary(Vtotal_p)
posterior_summary(V_total)

```

#Total additive variance of growth
Question: Do we need to account for the covariance among growth curve parameters? 
```{r}
Vtotal_a <- VCV.3.2.DA[,"(Intercept):(Intercept).liz_id"]  + #lizard variance in intercept
  VCV.3.2.DA[,"z_days_since_hatch:z_days_since_hatch.liz_id"] + #lizard variance in slope
  VCV.3.2.DA[,"I(z_days_since_hatch^2):I(z_days_since_hatch^2).liz_id"]  #lizard variance in curve

# Yes, whether we need to account for covariance here is a little uncertain. If we want the total genetic variance in growth in an average environment, I would think we need to account for the covariance as well.


  Var_a <- data.frame(VCV.3.2.DA) %>%
              select(c(1,5,9))       # Just the variances for A
  Cov_a <- data.frame(VCV.3.2.DA) %>%
              select(c(2:4,6:8))     # Just the covariance for A

  V_a <- rowSums(Var_a) + rowSums(2*Cov_a)

# Genetic variation in growth

  Growth_G <- V_a / V_total
  posterior_summary(Growth_G)


posterior_summary(Vtotal_a)
```

#Narrow sense Heritability of growth (all parameters)
h2 = Va / (Vp 
Question: Do we need to account for the covariance among growth curve parameters? 
```{r}
h2_growth <- Vtotal_a / Vtotal_p

posterior_summary(h2_growth)
```

#What if we wanted to additive genetic variance of specific growth parametrs and calculate heritability for each parameter? 
Question: Do we need to account for the covariance among growth curve parameters?
Question: What variance components should be in the denominator? If just calculating intercept only heritabilty, do we just have intercept only variance components in the denominator? As code below - this method is somewhat like calculating Rslope in my first chapter.

```{r}
#Intercept
h2_intercept <- VCV.3.2.DA[,"(Intercept):(Intercept).liz_id"] / ( VCV.3.2.DA[,"(Intercept):(Intercept).liz_id"] +
                                                                    VCV.3.2.DA[,"(Intercept):(Intercept).dam_id"] +
                                                                    VCV.3.2.DA[,"units"] )

posterior_summary(h2_intercept) #Values seem quite high? 

#Slope
h2_slope <- VCV.3.2.DA[,"z_days_since_hatch:z_days_since_hatch.liz_id"] / ( VCV.3.2.DA[,"z_days_since_hatch:z_days_since_hatch.liz_id"] +
                                                                              VCV.3.2.DA[,"z_days_since_hatch:z_days_since_hatch.dam_id"] +
                                                                              VCV.3.2.DA[,"units"] )
posterior_summary(h2_slope) #Values seem quite high? 

#etc for curvature
```

Alternatively, do we still have Vtotal_p (id intercept, id slope, id curve, dam intercept, dam slope, dam curve and residuals) as the denominator when we are calculating heritability? 
Question: Do we need to account for the covariance among growth curve parameters?

```{r}
#Intercept
h2_intercept_2 <- VCV.3.2.DA[,"(Intercept):(Intercept).liz_id"] / ( Vtotal_p)

posterior_summary(h2_intercept_2) #Values seem more sensible
```

