---
title: 'ESM brms text for ldeli growth'
author: Fonti Kar
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: "Style_guide.docx"
---

```{r setup, include=FALSE, eval = T, echo = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
sessionInfo()

# R version 3.6.1 (2019-07-05)
# Platform: x86_64-apple-darwin15.6.0 (64-bit)
# Running under: macOS High Sierra 10.13.6

pacman::p_load(dplyr, magrittr, ggplot2, patchwork, lubridate, stringr, tidyr, MCMCglmm, bookdown, pander, brms, latex2exp)

#Read in dataset
#Complete
data <- read.csv("~/Dropbox/1 - PhD/4 - ldeli_growthrate/data/growth/processed/analysis/Ldeli_quangen_growth.csv", stringsAsFactors = F)

#Augmented
data_DA <- read.csv("~/Dropbox/1 - PhD/4 - ldeli_growthrate/data/growth/processed/analysis/Ldeli_quangen_growth_DA.csv", stringsAsFactors = F)

#Functions
ztran_DsH <- function(day) {
  (day - mean(data$days_since_hatch, na.rm = T)) / sd(data$days_since_hatch, na.rm = T)
}

backztran_DSH <- function(z_day_since_hatch){
  (z_day_since_hatch * sd(data$days_since_hatch, na.rm = T)) + mean(data$days_since_hatch, na.rm = T)
}

source("~/Dropbox/1 - PhD/4 - ldeli_growthrate/R/Analysis/brms functions.R")

#ggplot theme
my_theme <- theme(#legend.position = "none",
  legend.position = "bottom",
  legend.text =element_text(size = 14),
  legend.title =element_text(size = 14, face = "bold"),
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(),
  axis.text=element_text(size=16),
  axis.title=element_text(size=16,face="bold"),
  plot.title = element_text(size = 20, face = "bold", hjust = 0.5))
```

## Model fitting and selection of random effects structure

To then test how G, M and h2 change across age, we used model selection to determine the most appropriate random effects structure for our data as we had no a priori knowledge of how the variance components change with age. We fitted seven models with varying complexity in their random effects and compared their WAIC values (Table S1). We fitted random intercepts and random slopes by including either a linear age term or both linear and quadratic age terms to partition variance across age. Two models were equally supported, the first included a random linear and quadratic slope for G and M and PE. (Model 3, Table S1) and the second included a random linear and quadratic slope for G and M and a random intercept for PE (Model 7, Table S1). To avoid overfitting, we selected the more parsimonious model and used this random effect structure for the remaining analysis unless stated otherwise (Model 7).

```{r, random effects, echo = FALSE, warning = FALSE, include = FALSE}
#Read in models
mod.1 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_4.5")
mod.2 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_4.2")
mod.3 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_4.1")
mod.4 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_4.4")
mod.5 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_4.3")
mod.6 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_4.6")
mod.7 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_5.6")

#Add waics
w_mod.1 <- waic(mod.1)
w_mod.2 <- waic(mod.2)
w_mod.3 <- waic(mod.3)
w_mod.4 <- waic(mod.4)
w_mod.5 <- waic(mod.5)
w_mod.6 <- waic(mod.6)
w_mod.7 <- waic(mod.7)

#Add loo
loo_mod.1 <- loo(mod.1)
loo_mod.2 <- loo(mod.2)
loo_mod.3 <- loo(mod.3)
loo_mod.4 <- loo(mod.4)
loo_mod.5 <- loo(mod.5)
loo_mod.6 <- loo(mod.6)
loo_mod.7 <- loo(mod.7)

#Compare
loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)
loo_compare(loo_mod.1, loo_mod.2, loo_mod.3, loo_mod.4, loo_mod.5, loo_mod.6, loo_mod.7)

#Tabulating
random_waic <- data.frame(matrix(nrow = 7, ncol = 4))
colnames(random_waic) <- c("Model", "wAIC", "elpd_diff", "se_diff")

random_waic[1,1] <- c("Model 3 - quadratic slopes for G, M, PE") 
random_waic[2,1] <- c("Model 7 - intercept for PE, quadratic slopes for G, M")
random_waic[3,1] <- c("Model 4 - intercept for G, linear slopes for M, PE")
random_waic[4,1] <- c("Model 2 - linear slopes for G, M, PE") 
random_waic[5,1] <- c("Model 6 - intercept for PE, linear slopes for G, M")
random_waic[6,1] <- c("Model 5 - intercept for M, linear slopes for G, PE")
random_waic[7,1] <- c("Model 1 - intercepts for G, M, PE")

#wAIC values
random_waic[1,2] <- w_mod.3$estimates[3,1]
random_waic[2,2] <- w_mod.7$estimates[3,1]
random_waic[3,2] <- w_mod.4$estimates[3,1]
random_waic[4,2] <- w_mod.2$estimates[3,1]
random_waic[5,2] <- w_mod.6$estimates[3,1]
random_waic[6,2] <- w_mod.5$estimates[3,1]
random_waic[7,2] <- w_mod.1$estimates[3,1]

#Expected log predictive density diff
random_waic[1,3] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[1,1]
random_waic[2,3] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[2,1]
random_waic[3,3] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[3,1]
random_waic[4,3] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[4,1]
random_waic[5,3] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[5,1]
random_waic[6,3] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[6,1]
random_waic[7,3] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[7,1]

#SE diff
random_waic[1,4] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[1,2]
random_waic[2,4] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[2,2]
random_waic[3,4] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[3,2]
random_waic[4,4] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[4,2]
random_waic[5,4] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[5,2]
random_waic[6,4] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[6,2]
random_waic[7,4] <- loo_compare(w_mod.1, w_mod.2, w_mod.3, w_mod.4, w_mod.5, w_mod.6, w_mod.7)[7,2]
```

```{r, echo = FALSE}
pander(random_waic,
       justify = "lccc",
       #split.cell = 80,
       caption = "Table S1 Comparisons of wAIC values for seven models with different combinations of random effects structures for additive genetic variance, maternal variance and permanent environmental variance")
```

#Does our data have heterogenous residual variance?

Residual variance may conflate with estimates of other variance components if it changes over time (heterogenous variance) and is not properly accounted for. We therefore explicitly modelled residual variance to verify if this was the case using WAIC values. We fitted two models, both of which had the same fixed and random effects structure as Model 7 described above. The first model had homogenous residual variance whereas in the second model we modelled residual variance with a linear slope thereby allowing it to vary with age (see code for more details). The model with heterogenous variance was best supported (Table S2), we therefore modelled heterogenous variance in all subsequent models unless stated otherwise

```{r, echo = FALSE, warning = FALSE, include = FALSE}
brm_5.6 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_5.6") #Homo ***Currently running longer more nits version
brm_5.5 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_5.5") #Hetero 

#Add waics
w_mod.5.6 <- waic(brm_5.6)
w_mod.5.5 <- waic(brm_5.5)

#Add loo
loo_mod.5.6 <- loo(brm_5.6)
loo_mod.5.5 <- loo(brm_5.5)

#Compare
loo_compare(w_mod.5.6, w_mod.5.5)
loo_compare(loo_mod.5.6, loo_mod.5.5)

#Estimates
w_mod.5.6$estimates
w_mod.5.5$estimates[3,1]

#Summary of best supported model
summary(brm_5.5) 

#Summarising the LOO and wAIC of brm models
#Create a table
brms_IC <- as.data.frame(matrix(ncol =4, nrow = 2))
colnames(brms_IC) <- c("Model", "WAIC", "ELPD diff", "SE diff")
brms_IC$Model <- c("Heterogenous variance", "Homogenous variance")

#Fill in the table
#Heterogenous
brms_IC[1,2] <- w_mod.5.5$estimates[3,1]
brms_IC[1,3] <- loo_compare(w_mod.5.5, w_mod.5.6)[[1]]
brms_IC[1,4] <- loo_compare(w_mod.5.5, w_mod.5.6)[[3]]

#Homogenous
brms_IC[2,2] <- w_mod.5.6$estimates[3,1]
brms_IC[2,3] <- loo_compare(w_mod.5.5, w_mod.5.6)[[2]]
brms_IC[2,4] <- loo_compare(w_mod.5.5, w_mod.5.6)[[4]]
```

```{r, echo = FALSE}
# panderOptions('round',Inf)
# panderOptions('digits',7)

pander(x = brms_IC, 
       split.cell = 80,
       split.table = Inf,
       justify = "lccc",
       caption = "Table S2 Comparisons of expected log predictive density values for LOO and WAIC values to test the importance of  heterogenous and homogenous residual variance. Note that difference in values are calculated by substracting values from the model with lowest LOO and WAIC values i.e. the heterogenous variance model")
```

## The influence of developmental temperature on additive genetic variance and maternal effects across age 

We fitted random intercepts for $G$, $M$, $PE$ and $R$ to estimate the overall estimate across age. We found that additive genetic variance, permanent environmental variance and heritability of growth appears to be higher in the hot developmental temperature treatment however, there were no significant differences among treatment groups (Table S3). For each treatment group, we fitted an intercept in our fixed effects and used the best supported random effect structure (Model 7) with heterogenous residual variance. We found that additive genetic variance decreased upon emergence and remained relatively low and remained constant until approximately nine months of age, after which it increased rapidly (Fig. S1). Maternal effects followed a similar pattern, decreasing sharply upon hatching and dropped to the minimum at approximately six months before it increased (Fig. S1).  Residual variance in cold incubated lizards showed a reasonably shallow increase  whereas it increased more steeply in hot incubated lizard (Fig. S1). The $G$ and $M$ matrices for each treatment group are presented in Table S4-S5.

```{r, echo = FALSE, include = FALSE}
#Marginalised over age - PIE CHART
#Read in intercept models
cold_brm_4.5 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/cold_brm_4.5")
hot_brm_4.5 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/hot_brm_4.5")

#Extract VCV
cold_brm_4.5_post <- posterior_samples(cold_brm_4.5) 
hot_brm_4.5_post <- posterior_samples(hot_brm_4.5) 

#Hot treatment
hot_brm_4.5_post[,"sd_id__Intercept"] %>% posterior_summary() #G Variance
hot_brm_4.5_post[,"sd_dam_id__Intercept"] %>% posterior_summary() #Dam Variance
hot_brm_4.5_post[,"sd_liz_id__Intercept"] %>% posterior_summary() #PE Variance

Hot_Pheno_intercept <- hot_brm_4.5_post[,"sd_id__Intercept"] +
  hot_brm_4.5_post[,"sd_dam_id__Intercept"] + 
  hot_brm_4.5_post[,"sd_liz_id__Intercept"] + 
  hot_brm_4.5_post[,"sigma"]

#Hot Heritability
hot_h2 <- (hot_brm_4.5_post[,"sd_id__Intercept"] / Hot_Pheno_intercept) 
posterior_summary(hot_h2)[,-2] %>% round(2)

#Cold treatment
cold_brm_4.5_post[,"sd_id__Intercept"] %>% posterior_summary() #G Variance
cold_brm_4.5_post[,"sd_dam_id__Intercept"] %>% posterior_summary() #Dam Variance
cold_brm_4.5_post[,"sd_liz_id__Intercept"] %>% posterior_summary() #PE Variance

cold_Pheno_intercept <- cold_brm_4.5_post[,"sd_id__Intercept"] +
  cold_brm_4.5_post[,"sd_dam_id__Intercept"] + 
  cold_brm_4.5_post[,"sd_liz_id__Intercept"] + 
  cold_brm_4.5_post[,"sigma"]

#cold Heritability
cold_h2 <- (cold_brm_4.5_post[,"sd_id__Intercept"]/ cold_Pheno_intercept)
posterior_summary(cold_h2)[,-2] %>% round(2)

#Create a table
hot_cold_Vcomps <- as.data.frame(matrix(ncol = 5, nrow = 10))
colnames(hot_cold_Vcomps) <- c("Treatment", "Variable", "Estimate", "Lower", "Upper")

hot_cold_Vcomps$Treatment <- rep(c("Hot", "Cold"), each =5)
hot_cold_Vcomps$Variable <-rep(c("V_additive_g", "V_maternal", "V_pe", "Vresidual", "h2"), 2)

#Fill in table
hot_cold_Vcomps[1,3:5] <- (hot_brm_4.5_post[,"sd_id__Intercept"] %>% posterior_summary())[-2] %>% round(3)
hot_cold_Vcomps[2,3:5] <- (hot_brm_4.5_post[,"sd_dam_id__Intercept"] %>% posterior_summary())[-2]%>% round(3)
hot_cold_Vcomps[3,3:5] <- (hot_brm_4.5_post[,"sd_liz_id__Intercept"] %>% posterior_summary())[-2]%>% round(3)
hot_cold_Vcomps[4,3:5] <- (hot_brm_4.5_post[,"sigma"] %>% posterior_summary())[-2]%>% round(3)
hot_cold_Vcomps[5,3:5] <- ((hot_brm_4.5_post[,"sd_id__Intercept"] / Hot_Pheno_intercept) %>% posterior_summary())[-2]%>% round(3)

hot_cold_Vcomps[6,3:5] <- (cold_brm_4.5_post[,"sd_id__Intercept"] %>% posterior_summary())[-2]%>% round(3)
hot_cold_Vcomps[7,3:5] <- (cold_brm_4.5_post[,"sd_dam_id__Intercept"] %>% posterior_summary())[-2]%>% round(3)
hot_cold_Vcomps[8,3:5] <- (cold_brm_4.5_post[,"sd_liz_id__Intercept"] %>% posterior_summary())[-2]%>% round(3)
hot_cold_Vcomps[9,3:5] <- (cold_brm_4.5_post[,"sigma"] %>% posterior_summary())[-2]%>% round(3)
hot_cold_Vcomps[10,3:5] <- ((cold_brm_4.5_post[,"sd_id__Intercept"] / cold_Pheno_intercept) %>% posterior_summary())[-2]%>% round(3)

```

```{r, echo = FALSE}
pander(hot_cold_Vcomps,
       split.cell = c(100,30,30,30,30),
       split.table = Inf,
       justify = "clccc",
       caption = "Table S3 Treatment comparisons of additive genetic variance, maternal variance, permanent environmental variance and heritability. These are estimated from a model where random intercepts were fitted for both accounts of lizard identity and dam identity")
```

```{r, echo = FALSE}
#Figure of variance components G M E over age
cold_brm_5.5 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/cold_brm_5.5") 
hot_brm_5.5 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/hot_brm_5.5")

#Define the days
z_days <- ztran_DsH(seq(0, 500, 30))

#Lapply to get numbers across days
brms_hot_Vg <- lapply(z_days, function(x) brms_Vcomp(model = hot_brm_5.5, x = x, group_var = "liz_id")) %>% bind_rows()
brms_hot_Vm <- lapply(z_days, function(x) brms_Vcomp(model = hot_brm_5.5, x = x, group_var = "dam_id")) %>% bind_rows()
brms_hot_Ve <- lapply(z_days, function(x) brms_Vcomp(model = hot_brm_5.5, x = x, group_var = "sigma")) %>% bind_rows()

brms_hot <- bind_rows(brms_hot_Vg,
                      brms_hot_Vm,
                      brms_hot_Ve)

brms_hot$treatment <- "hot"

brms_cold_Vg <- lapply(z_days, function(x) brms_Vcomp(model = cold_brm_5.5, x = x, group_var = "liz_id")) %>% bind_rows()
brms_cold_Vm <- lapply(z_days, function(x) brms_Vcomp(model = cold_brm_5.5, x = x, group_var = "dam_id")) %>% bind_rows()
brms_cold_Ve <- lapply(z_days, function(x) brms_Vcomp(model = cold_brm_5.5, x = x, group_var = "sigma")) %>% bind_rows()

brms_cold <- bind_rows(brms_cold_Vg,
                       brms_cold_Vm,
                       brms_cold_Ve)

brms_cold$treatment <- "cold"

brms_compare <- bind_rows(brms_hot, brms_cold)

#Figure of variance compones G M E over age
group_var_labs_3 <- c("G  ", "M  ", "Residual")

names(group_var_labs_3) <- unique(brms_compare$group_id)

#Change order
brms_compare$group_id<- factor(brms_compare$group_id , levels = c("liz_id", "dam_id", "sigma"))
brms_compare$treatment<- factor(brms_compare$treatment , levels = c("cold", "hot"), labels = c("Cold", "Hot"))
```
```{r, echo = FALSE, warning = FALSE, message = FALSE}
ggplot(data = brms_compare, aes(x = day, y = Estimate, colour = factor(treatment))) +
  geom_point(size = 2) + 
  #geom_errorbar(aes(min = Lower, max = Upper), width = 0, alpha = 0.5) + 
  geom_ribbon(aes(ymin = Lower, ymax = Upper), alpha = 0.05) +
  #geom_smooth(aes(ymin = Lower, ymax = Upper), stat = "identity", alpha = 0.1) +
  #geom_line() + 
  stat_smooth(method = "auto", se = F, size = 1) + 
  facet_wrap(~group_id, scales = "free_y", labeller = labeller(group_id = group_var_labs_3)) + 
  scale_x_continuous(breaks = seq(0, 500, 60)) + 
  #scale_colour_manual(values = c("#5BBCD6", "#F98400")) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) + 
  labs(x = "Age",
       y = "Variance of Mass",
       #title = "Relative contribution of variance over age",
       colour =  "Treatment") + 
  theme_bw() + 
  my_theme +
  theme(legend.position = "none",
        strip.text = element_text(size = 18),
        strip.background = element_blank())
```

```{r, echo = FALSE, include= FALSE}
#Compiling G matrix for hot incubated lizards

#Calculate VAR from SD
hot_G_sd_post <- posterior_samples(hot_brm_5.5, "^sd_liz_id")
hot_G_var_post <- posterior_samples(hot_brm_5.5, "^sd_liz_id")^2
hot_G_var_summary <- posterior_summary(hot_G_var_post)[,-2] %>% round(3)

#Calculate COV from COR
hot_G_cor_post <- posterior_samples(hot_brm_5.5, "^cor_liz_id")
hot_G_cor_summary <- posterior_summary(hot_G_cor_post)[,-2] %>% signif(digits = 3)

hot_G_cov_post <- cbind(hot_G_cor_post[1] * (hot_G_sd_post[1] * hot_G_sd_post[2]), 
                  hot_G_cor_post[2] * (hot_G_sd_post[1] * hot_G_sd_post[3]),
                  hot_G_cor_post[3] * (hot_G_sd_post[2] * hot_G_sd_post[3]))
names(hot_G_cov_post) <- str_replace(names(hot_G_cor_post), "cor", "cov")
hot_G_cov_summary <- posterior_summary(hot_G_cov_post)[,-2] %>% signif(digits = 3)

#Tabulating
Table_4_G <- data.frame(matrix(nrow = 3, ncol = 3))
#Names
colnames(Table_4_G) <- rownames(Table_4_G) <- c("Intercept", "Linear Slope", "Quadratic Slope")

#Fill in matrix - diagonals 
Table_4_G[1, 1] <- paste0(hot_G_var_summary[1,1], " (", hot_G_var_summary[1,2], " - ", hot_G_var_summary[1,3], ")")
Table_4_G[2, 2] <- paste0(hot_G_var_summary[2,1], " (", hot_G_var_summary[2,2], " - ", hot_G_var_summary[2,3], ")")
Table_4_G[3, 3] <- paste0(hot_G_var_summary[3,1], " (", hot_G_var_summary[3,2], " - ", hot_G_var_summary[3,3], ")")

#upper off-diagonals - covariances
Table_4_G[1, 2] <- paste0(hot_G_cov_summary[1,1], " (", hot_G_cov_summary[1,2], " - ", hot_G_cov_summary[1,3], ")")
Table_4_G[1, 3] <- paste0(hot_G_cov_summary[2,1], " (", hot_G_cov_summary[2,2], " - ", hot_G_cov_summary[2,3], ")")
Table_4_G[2, 3] <- paste0(hot_G_cov_summary[3,1], " (", hot_G_cov_summary[3,2], " - ", hot_G_cov_summary[3,3], ")")

#lower off diagonals - correlations 
Table_4_G[2, 1] <- paste0(hot_G_cor_summary[1,1], " (", hot_G_cor_summary[1,2], " - ", hot_G_cor_summary[1,3], ")")
Table_4_G[3, 1] <- paste0(hot_G_cor_summary[2,1], " (", hot_G_cor_summary[2,2], " - ", hot_G_cor_summary[2,3], ")")
Table_4_G[3, 2] <- paste0(hot_G_cor_summary[3,1], " (", hot_G_cor_summary[3,2], " - ", hot_G_cor_summary[3,3], ")")

#write.csv(Table_4_G, "output/tabs/Table_4_G_brms_hot.csv")
```

```{r, echo = FALSE, include= FALSE}
#Compiling M matrix for hot incubated lizards

#Calculate VAR from SD
hot_M_sd_post <- posterior_samples(hot_brm_5.5, "^sd_dam_id")
hot_M_var_post <- posterior_samples(hot_brm_5.5, "^sd_dam_id")^2
hot_M_var_summary <- posterior_summary(hot_M_var_post)[,-2] %>% round(3)

#Calculate COV from COR
hot_M_cor_post <- posterior_samples(hot_brm_5.5, "^cor_dam_id")
hot_M_cor_summary <- posterior_summary(hot_M_cor_post)[,-2] %>% signif(digits = 3)

hot_M_cov_post <- cbind(hot_M_cor_post[1] * (hot_M_sd_post[1] * hot_M_sd_post[2]), 
                  hot_M_cor_post[2] * (hot_M_sd_post[1] * hot_M_sd_post[3]),
                  hot_M_cor_post[3] * (hot_M_sd_post[2] * hot_M_sd_post[3]))
names(hot_M_cov_post) <- str_replace(names(hot_M_cor_post), "cor", "cov")
hot_M_cov_summary <- posterior_summary(hot_M_cov_post)[,-2] %>% signif(digits = 3)

#Tabulating
Table_4_M <- data.frame(matrix(nrow = 3, ncol = 3))
#Names
colnames(Table_4_M) <- rownames(Table_4_M) <- c("Intercept", "Linear Slope", "Quadratic Slope")

#Fill in matrix - diagonals 
Table_4_M[1, 1] <- paste0(hot_M_var_summary[1,1], " (", hot_M_var_summary[1,2], " - ", hot_M_var_summary[1,3], ")")
Table_4_M[2, 2] <- paste0(hot_M_var_summary[2,1], " (", hot_M_var_summary[2,2], " - ", hot_M_var_summary[2,3], ")")
Table_4_M[3, 3] <- paste0(hot_M_var_summary[3,1], " (", hot_M_var_summary[3,2], " - ", hot_M_var_summary[3,3], ")")

#upper off-diagonals - covariances
Table_4_M[1, 2] <- paste0(hot_M_cov_summary[1,1], " (", hot_M_cov_summary[1,2], " - ", hot_M_cov_summary[1,3], ")")
Table_4_M[1, 3] <- paste0(hot_M_cov_summary[2,1], " (", hot_M_cov_summary[2,2], " - ", hot_M_cov_summary[2,3], ")")
Table_4_M[2, 3] <- paste0(hot_M_cov_summary[3,1], " (", hot_M_cov_summary[3,2], " - ", hot_M_cov_summary[3,3], ")")

#lower off diagonals - correlations 
Table_4_M[2, 1] <- paste0(hot_M_cor_summary[1,1], " (", hot_M_cor_summary[1,2], " - ", hot_M_cor_summary[1,3], ")")
Table_4_M[3, 1] <- paste0(hot_M_cor_summary[2,1], " (", hot_M_cor_summary[2,2], " - ", hot_M_cor_summary[2,3], ")")
Table_4_M[3, 2] <- paste0(hot_M_cor_summary[3,1], " (", hot_M_cor_summary[3,2], " - ", hot_M_cor_summary[3,3], ")")

#write.csv(Table_4_M, "output/tabs/Table_4_M_brms_hot.csv")

#PE
posterior_samples(hot_brm_5.5, "^sd_id")^2 %>% posterior_summary() %>% signif(digits = 3)

#Residuals
posterior_samples(hot_brm_5.5, "b_sigma_I")^2 %>% posterior_summary() %>% signif(digits = 3)
posterior_summary(hot_brm_5.5, "b_sigma_z") %>% signif(digits = 3)

```

```{r, echo = FALSE, include= FALSE}
#Compiling G matrix for cold incubated lizards

#Calculate VAR from SD
cold_G_sd_post <- posterior_samples(cold_brm_5.5, "^sd_liz_id")
cold_G_var_post <- posterior_samples(cold_brm_5.5, "^sd_liz_id")^2
cold_G_var_summary <- posterior_summary(cold_G_var_post)[,-2] %>% round(3)

#Calculate COV from COR
cold_G_cor_post <- posterior_samples(cold_brm_5.5, "^cor_liz_id")
cold_G_cor_summary <- posterior_summary(cold_G_cor_post)[,-2] %>% signif(digits = 3)

cold_G_cov_post <- cbind(cold_G_cor_post[1] * (cold_G_sd_post[1] * cold_G_sd_post[2]), 
                  cold_G_cor_post[2] * (cold_G_sd_post[1] * cold_G_sd_post[3]),
                  cold_G_cor_post[3] * (cold_G_sd_post[2] * cold_G_sd_post[3]))
names(cold_G_cov_post) <- str_replace(names(cold_G_cor_post), "cor", "cov")
cold_G_cov_summary <- posterior_summary(cold_G_cov_post)[,-2] %>% signif(digits = 3)

#Tabulating
Table_5_G <- data.frame(matrix(nrow = 3, ncol = 3))
#Names
colnames(Table_5_G) <- rownames(Table_5_G) <- c("Intercept", "Linear Slope", "Quadratic Slope")

#Fill in matrix - diagonals 
Table_5_G[1, 1] <- paste0(cold_G_var_summary[1,1], " (", cold_G_var_summary[1,2], " - ", cold_G_var_summary[1,3], ")")
Table_5_G[2, 2] <- paste0(cold_G_var_summary[2,1], " (", cold_G_var_summary[2,2], " - ", cold_G_var_summary[2,3], ")")
Table_5_G[3, 3] <- paste0(cold_G_var_summary[3,1], " (", cold_G_var_summary[3,2], " - ", cold_G_var_summary[3,3], ")")

#upper off-diagonals - covariances
Table_5_G[1, 2] <- paste0(cold_G_cov_summary[1,1], " (", cold_G_cov_summary[1,2], " - ", cold_G_cov_summary[1,3], ")")
Table_5_G[1, 3] <- paste0(cold_G_cov_summary[2,1], " (", cold_G_cov_summary[2,2], " - ", cold_G_cov_summary[2,3], ")")
Table_5_G[2, 3] <- paste0(cold_G_cov_summary[3,1], " (", cold_G_cov_summary[3,2], " - ", cold_G_cov_summary[3,3], ")")

#lower off diagonals - correlations 
Table_5_G[2, 1] <- paste0(cold_G_cor_summary[1,1], " (", cold_G_cor_summary[1,2], " - ", cold_G_cor_summary[1,3], ")")
Table_5_G[3, 1] <- paste0(cold_G_cor_summary[2,1], " (", cold_G_cor_summary[2,2], " - ", cold_G_cor_summary[2,3], ")")
Table_5_G[3, 2] <- paste0(cold_G_cor_summary[3,1], " (", cold_G_cor_summary[3,2], " - ", cold_G_cor_summary[3,3], ")")

#write.csv(Table_5_G, "output/tabs/Table_5_G_G_brms_cold.csv")
```

```{r, echo = FALSE, include= FALSE}
#Compiling M matrix for cold incubated lizards

#Calculate VAR from SD
cold_M_sd_post <- posterior_samples(cold_brm_5.5, "^sd_dam_id")
cold_M_var_post <- posterior_samples(cold_brm_5.5, "^sd_dam_id")^2
cold_M_var_summary <- posterior_summary(cold_M_var_post)[,-2] %>% round(3)

#Calculate COV from COR
cold_M_cor_post <- posterior_samples(cold_brm_5.5, "^cor_dam_id")
cold_M_cor_summary <- posterior_summary(cold_M_cor_post)[,-2] %>% signif(digits = 3)

cold_M_cov_post <- cbind(cold_M_cor_post[1] * (cold_M_sd_post[1] * cold_M_sd_post[2]), 
                  cold_M_cor_post[2] * (cold_M_sd_post[1] * cold_M_sd_post[3]),
                  cold_M_cor_post[3] * (cold_M_sd_post[2] * cold_M_sd_post[3]))
names(cold_M_cov_post) <- str_replace(names(cold_M_cor_post), "cor", "cov")
cold_M_cov_summary <- posterior_summary(cold_M_cov_post)[,-2] %>% signif(digits = 3)

#Tabulating
Table_5_M <- data.frame(matrix(nrow = 3, ncol = 3))
#Names
colnames(Table_5_M) <- rownames(Table_5_M) <- c("Intercept", "Linear Slope", "Quadratic Slope")

#Fill in matrix - diagonals 
Table_5_M[1, 1] <- paste0(cold_M_var_summary[1,1], " (", cold_M_var_summary[1,2], " - ", cold_M_var_summary[1,3], ")")
Table_5_M[2, 2] <- paste0(cold_M_var_summary[2,1], " (", cold_M_var_summary[2,2], " - ", cold_M_var_summary[2,3], ")")
Table_5_M[3, 3] <- paste0(cold_M_var_summary[3,1], " (", cold_M_var_summary[3,2], " - ", cold_M_var_summary[3,3], ")")

#upper off-diagonals - covariances
Table_5_M[1, 2] <- paste0(cold_M_cov_summary[1,1], " (", cold_M_cov_summary[1,2], " - ", cold_M_cov_summary[1,3], ")")
Table_5_M[1, 3] <- paste0(cold_M_cov_summary[2,1], " (", cold_M_cov_summary[2,2], " - ", cold_M_cov_summary[2,3], ")")
Table_5_M[2, 3] <- paste0(cold_M_cov_summary[3,1], " (", cold_M_cov_summary[3,2], " - ", cold_M_cov_summary[3,3], ")")

#lower off diagonals - correlations 
Table_5_M[2, 1] <- paste0(cold_M_cor_summary[1,1], " (", cold_M_cor_summary[1,2], " - ", cold_M_cor_summary[1,3], ")")
Table_5_M[3, 1] <- paste0(cold_M_cor_summary[2,1], " (", cold_M_cor_summary[2,2], " - ", cold_M_cor_summary[2,3], ")")
Table_5_M[3, 2] <- paste0(cold_M_cor_summary[3,1], " (", cold_M_cor_summary[3,2], " - ", cold_M_cor_summary[3,3], ")")

#write.csv(Table_5_M, "output/tabs/Table_5_M_brms_cold.csv")

#PE
posterior_samples(cold_brm_5.5, "^sd_id")^2 %>% posterior_summary() %>% signif(digits = 3)

#Residuals
posterior_samples(cold_brm_5.5, "b_sigma_I")^2 %>% posterior_summary() %>% signif(digits = 3)
posterior_summary(cold_brm_5.5, "b_sigma_z") %>% signif(digits = 3)
```

## Accounting for scale-effects using coefficients of variation

As the mean body mass increases over time, the variance may also increase concurrently due to scale effects and potentially bias estimates of quantitative genetics parameters (Wilson, Kruuk, et al., 2005). We therefore calculated coefficients of variation (CV) across age for each variance component using the following equation: 
$$CV_{x} = \displaystyle \frac{ 100 . V_{x}^{0.5} }{\mu_{age}}$$

where $CV_x$ is the CV for a given variance component e.g. $CV_M$ is the CV of maternal effects. The CV of maternal effects ($CV_M$) and $CV_G$ showed the same pattern as the raw variance estimates (Fig. S1-2). There were no treatment differences in $CV_G$, $CV_M$. $CV_R$ followed a quadratic relationship. Treatment differences in $CV_R$ were a lot less subtle compared to raw variance estimates and differences occured at particular ages, typically early and late in development (Fig. S2). 

```{r, echo = FALSE, include= FALSE}
#CV calculations of G M Sigma
hot_brm_5.4 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/hot_brm_5.4")
cold_brm_5.4 <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/cold_brm_5.4")

hot_CV_G <- lapply(seq(0, 500, 30), function(x) get_CV_brms(model = hot_brm_5.4, x = x, group_var = "liz_id")) %>% bind_rows()
hot_CV_M <- lapply(seq(0, 500, 30), function(x) get_CV_brms(model = hot_brm_5.4, x = x, group_var = "dam_id")) %>% bind_rows()
hot_CV_PE <- lapply(seq(0, 500, 30), function(x) get_CV_brms(model = hot_brm_5.4, x = x, group_var = "id")) %>% bind_rows()
hot_CV_E <- lapply(seq(0, 500, 30), function(x) get_CV_brms(model = hot_brm_5.4, x = x, group_var = "sigma")) %>% bind_rows()

hot_CV <- bind_rows(hot_CV_G, hot_CV_M, hot_CV_E)
hot_CV$treatment <- "Hot"

cold_CV_G <- lapply(seq(0, 500, 30), function(x) get_CV_brms(model = cold_brm_5.4, x = x, group_var = "liz_id")) %>% bind_rows()
cold_CV_M <- lapply(seq(0, 500, 30), function(x) get_CV_brms(model = cold_brm_5.4, x = x, group_var = "dam_id")) %>% bind_rows()
cold_CV_PE <- lapply(seq(0, 500, 30), function(x) get_CV_brms(model = cold_brm_5.4, x = x, group_var = "id")) %>% bind_rows()
cold_CV_E <- lapply(seq(0, 500, 30), function(x) get_CV_brms(model = cold_brm_5.4, x = x, group_var = "sigma")) %>% bind_rows()

cold_CV <- bind_rows(cold_CV_G, cold_CV_M, cold_CV_E)
cold_CV$treatment <- "Cold"

#Putting the hot and cold data together
brms_CV_compare <- bind_rows(hot_CV, cold_CV)
```

```{r, echo = FALSE, warning = FALSE, include = FALSE, message = FALSE}
#Plotting
ggplot(data = brms_CV_compare %>% filter(!group_id == "sigma"), aes(x = day, y = Estimate, colour = factor(treatment))) +
  geom_point(size = 2) + 
  #geom_errorbar(aes(min = Lower, max = Upper), width = 0, alpha = 0.5) + 
  geom_ribbon(aes(ymin = Lower, ymax = Upper), alpha = 0.05) +
  #geom_smooth(aes(ymin = Lower, ymax = Upper), stat = "identity", alpha = 0.1) +
  #geom_line() + 
  stat_smooth(method = "auto", se = F, size = 1) + 
  facet_wrap(~group_id, scales = "free_y", labeller = labeller(group_id = group_var_labs_3)) + 
  scale_x_continuous(breaks = seq(0, 500, 60)) + 
  #scale_colour_manual(values = c("#5BBCD6", "#F98400")) + 
  scale_colour_manual(values = c("#2790F3", "#F24D2A")) + 
  labs(x = "Age",
       y = "CV of Mass",
       #title = "Relative contribution of variance over age",
       colour =  "Treatment") + 
  theme_bw() + 
  my_theme +
  theme(legend.position = "none",
        strip.text = element_text(size = 18),
        strip.background = element_blank())
```

## Do growth trajectories differ among developmental temperatures?

We fitted four models with different combinations of treatment interactions with the linear and quadratic components of the growth curve . Coefficient estimates for all models are provided in Table. S5-9. The G and M matrix for the best supported model is presented in Table S6.

```{r, echo = FALSE, include = FALSE}
#Compiling fixed effects coefficients for overall model testing for differences in growth curves
brm_5.het <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_5.het")
brm_5.het_post <- posterior_samples(brm_5.het)
colnames(brm_5.het_post)[1:21]

#Combining the coefficients from the final model
brm_5.fixed <- brm_5.het_post[,c(1,3,4,5,6,7)] %>% posterior_summary() %>% round(3) 
brm_5.fixed <- brm_5.fixed[,c(1,3,4)]
```

```{r, echo = FALSE}
Table_5 <- brm_5.fixed %>% as.data.frame()
rownames(Table_5) <- c("Intercept", "Treatment", "Age",  "Age^2", "Treatment x Age","Treatment x Age^2")

Table_5$Parameter <- rownames(Table_5)
rownames(Table_5) <- NULL
Table_5 <- select(Table_5, Parameter, Estimate:Q97.5)

pander(Table_5,
       split.cell = c(100,30,30,30),
       #split.table = Inf,
       justify = "lccc",
       caption = "Table S5 Coefficient estimates from full model testing the effects of developmental treatment on mass and how mass changes with age. Bolded estimates are significantly different from zero. * indicates that value is above zero prior to rounding. n_obs = 3002")
```

```{r, echo = FALSE, include = FALSE}
#Compiling G matrix for best supported model (5_het)

colnames(brm_5.het_post)[1:21]

#Calculate VAR from SD
G_sd_post <- posterior_samples(brm_5.het, "^sd_liz_id")
G_var_post <- posterior_samples(brm_5.het, "^sd_liz_id")^2
G_var_summary <- posterior_summary(G_var_post)[,-2] %>% round(3)

#Calculate COV from COR
G_cor_post <- posterior_samples(brm_5.het, "^cor_liz_id")
G_cor_post
G_cor_summary <- posterior_summary(G_cor_post)[,-2] %>% signif(digits = 3)

G_cov_post <- cbind(G_cor_post[1] * (G_sd_post[1] * G_sd_post[2]), 
                  G_cor_post[2] * (G_sd_post[1] * G_sd_post[3]),
                  G_cor_post[3] * (G_sd_post[2] * G_sd_post[3]))
names(G_cov_post) <- str_replace(names(G_cor_post), "cor", "cov")
G_cov_summary <- posterior_summary(G_cov_post)[,-2] %>% signif(digits = 3)

#Tabulating
Table_6_G <- data.frame(matrix(nrow = 3, ncol = 3))
#Names
colnames(Table_6_G) <- rownames(Table_6_G) <-  c("Intercept", "Linear Slope", "Quadratic Slope")

#Fill in matrix - diagonals 
Table_6_G[1, 1] <- paste0(G_var_summary[1,1], " (", G_var_summary[1,2], " - ", G_var_summary[1,3], ")")
Table_6_G[2, 2] <- paste0(G_var_summary[2,1], " (", G_var_summary[2,2], " - ", G_var_summary[2,3], ")")
Table_6_G[3, 3] <- paste0(G_var_summary[3,1], " (", G_var_summary[3,2], " - ", G_var_summary[3,3], ")")

#upper off-diagonals - covariances
Table_6_G[1, 2] <- paste0(G_cov_summary[1,1], " (", G_cov_summary[1,2], " - ", G_cov_summary[1,3], ")")
Table_6_G[1, 3] <- paste0(G_cov_summary[2,1], " (", G_cov_summary[2,2], " - ", G_cov_summary[2,3], ")")
Table_6_G[2, 3] <- paste0(G_cov_summary[3,1], " (", G_cov_summary[3,2], " - ", G_cov_summary[3,3], ")")

#lower off diagonals - correlations 
Table_6_G[2, 1] <- paste0(G_cor_summary[1,1], " (", G_cor_summary[1,2], " - ", G_cor_summary[1,3], ")")
Table_6_G[3, 1] <- paste0(G_cor_summary[2,1], " (", G_cor_summary[2,2], " - ", G_cor_summary[2,3], ")")
Table_6_G[3, 2] <- paste0(G_cor_summary[3,1], " (", G_cor_summary[3,2], " - ", G_cor_summary[3,3], ")")

#write.csv(Table_6_G, "output/tabs/Table_6_G.csv")
```

```{r, echo = FALSE, include = FALSE}
#Compiling M matrix for best supported model (5_het)
brm_5.het <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_5.het")
#Calculate VAR from SD
M_sd_post <- posterior_samples(brm_5.het, "^sd_dam_id")
M_var_post <- posterior_samples(brm_5.het, "^sd_dam_id")^2
M_var_summary <- posterior_summary(M_var_post)[,-2] %>% round(3)

#Calculate COV from COR
M_cor_post <- posterior_samples(brm_5.het, "^cor_dam_id")
M_cor_summary <- posterior_summary(M_cor_post)[,-2] %>% signif(digits = 3)

M_cov_post <- cbind(M_cor_post[1] * (M_sd_post[1] * M_sd_post[2]), 
                  M_cor_post[2] * (M_sd_post[1] * M_sd_post[3]),
                  M_cor_post[3] * (M_sd_post[2] * M_sd_post[3]))
names(M_cov_post) <- str_replace(names(M_cor_post), "cor", "cov")
M_cov_summary <- posterior_summary(M_cov_post)[,-2] %>% signif(digits = 3)

#Tabulating
Table_6_M <- data.frame(matrix(nrow = 3, ncol = 3))
#Names
colnames(Table_6_M) <- rownames(Table_6_M) <- c("Intercept", "Linear Slope", "Quadratic Slope")

#Fill in matrix - diagonals 
Table_6_M[1, 1] <- paste0(M_var_summary[1,1], " (", M_var_summary[1,2], " - ", M_var_summary[1,3], ")")
Table_6_M[2, 2] <- paste0(M_var_summary[2,1], " (", M_var_summary[2,2], " - ", M_var_summary[2,3], ")")
Table_6_M[3, 3] <- paste0(M_var_summary[3,1], " (", M_var_summary[3,2], " - ", M_var_summary[3,3], ")")

#upper off-diagonals - covariances
Table_6_M[1, 2] <- paste0(M_cov_summary[1,1], " (", M_cov_summary[1,2], " - ", M_cov_summary[1,3], ")")
Table_6_M[1, 3] <- paste0(M_cov_summary[2,1], " (", M_cov_summary[2,2], " - ", M_cov_summary[2,3], ")")
Table_6_M[2, 3] <- paste0(M_cov_summary[3,1], " (", M_cov_summary[3,2], " - ", M_cov_summary[3,3], ")")

#lower off diagonals - correlations 
Table_6_M[2, 1] <- paste0(M_cor_summary[1,1], " (", M_cor_summary[1,2], " - ", M_cor_summary[1,3], ")")
Table_6_M[3, 1] <- paste0(M_cor_summary[2,1], " (", M_cor_summary[2,2], " - ", M_cor_summary[2,3], ")")
Table_6_M[3, 2] <- paste0(M_cor_summary[3,1], " (", M_cor_summary[3,2], " - ", M_cor_summary[3,3], ")")

#write.csv(Table_6_M, "output/tabs/Table_6_M.csv")

#PE
posterior_samples(brm_5.het, "^sd_id")^2 %>% posterior_summary() %>% signif(digits = 3)

#Residuals
posterior_samples(brm_5.het, "b_sigma_I")^2 %>% posterior_summary() %>% signif(digits = 3)
posterior_summary(brm_5.het, "b_sigma_z") %>% signif(digits = 3)

```

```{r, echo = FALSE, include = FALSE}
#Model coefficients of the other models
brm_5.1.het <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_5.1.het")
brm_5.1.5.het <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_5.1.5.het")
brm_5.2.het <- readRDS("~/Dropbox/1 - PhD/4 - ldeli_growthrate/output/rds/brm_5.2.het")

#Posterior Summary
posterior_summary(brm_5.1.het)[1:20,] %>% round(3)
posterior_summary(brm_5.1.5.het)[1:20,] %>% round(3)
posterior_summary(brm_5.2.het)[1:19,] %>% round(3)
```

```{r, echo = FALSE}
Table_7 <- posterior_summary(brm_5.1.het)[1:20,-2] %>% round(3) %>% as.data.frame()
rownames(Table_7) <- c("Intercept", "Residual", "Treatment", "Age",  "Age^2", "Treatment x Age","Residual x Age",
                       "V_m intercept", "V_m  slope", "V_m curvature",
                       "V_pe",
                       "V_g intercept", "V_g slope", "V_g  curvature",
                       "Cor_m intercept - slope", "Cor_m intercept - curvature", "Cor_m slope - curvature",
                       "Cov_g intercept - slope", "Cov_g intercept - curvature", "Cov_g slope - curvature")

Table_7$Parameter <- rownames(Table_7)
rownames(Table_7) <- NULL
Table_7 <- select(Table_7, Parameter, Estimate:Q97.5)

pander(Table_7,
       split.cell = c(100,30,30,30),
       #split.table = Inf,
       justify = "lccc",
       caption = "Table S7 Coefficient estimates from model with interaction between treatment and age (linear growth rate) only. Bolded estimates are significantly different from zero. * indicates that value is above zero prior to rounding. n_obs = 3002")
```

```{r, echo = FALSE}
Table_8 <- posterior_summary(brm_5.1.5.het)[1:20,-2] %>% round(3) %>% as.data.frame()
rownames(Table_8) <- c("Intercept", "Residual", "Age", "Treatment",  "Age^2", "Treatment x Age^2","Residual x Age",
                       "V_m intercept", "V_m  slope", "V_m curvature",
                       "V_pe",
                       "V_g intercept", "V_g slope", "V_g  curvature",
                       "Cor_m intercept - slope", "Cor_m intercept - curvature", "Cor_m slope - curvature",
                       "Cov_g intercept - slope", "Cov_g intercept - curvature", "Cov_g slope - curvature")

Table_8$Parameter <- rownames(Table_8)
rownames(Table_8) <- NULL
Table_8 <- select(Table_8, Parameter, Estimate:Q97.5)

pander(Table_8,
       split.cell = c(100,30,30,30),
       #split.table = Inf,
       justify = "lccc",
       caption = "Table S8 Coefficient estimates from model with interaction between treatment and quadratic age paramater only. Bolded estimates are significantly different from zero. * indicates that value is above zero prior to rounding. n_obs = 3002")
```

```{r, echo = FALSE}
Table_9 <- posterior_summary(brm_5.2.het)[1:19,-2] %>% round(3) %>% as.data.frame()
rownames(Table_9) <- c("Intercept", "Residual", "Treatment", "Age",  "Age^2","Residual x Age",
                       "V_m intercept", "V_m  slope", "V_m curvature",
                       "V_pe",
                       "V_g intercept", "V_g slope", "V_g  curvature",
                       "Cor_m intercept - slope", "Cor_m intercept - curvature", "Cor_m slope - curvature",
                       "Cov_g intercept - slope", "Cov_g intercept - curvature", "Cov_g slope - curvature")

Table_9$Parameter <- rownames(Table_9)
rownames(Table_9) <- NULL
Table_9 <- select(Table_9, Parameter, Estimate:Q97.5)

pander(Table_9,
       split.cell = c(100,30,30,30),
       #split.table = Inf,
       justify = "lccc",
       caption = "Table S9 Coefficient estimates from model with main effects of treatment and age only. Bolded estimates are significantly different from zero. * indicates that value is above zero prior to rounding. n_obs = 3002")
```